Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-10 automatica/paper.tex
section 8

%\textcolor{red}{Iury: can you please describe the benchmarks?}

@@

%There are two continuous stirred tank reactor models named 
\textit{cstr} (\#11) and \textit{cstrtmp} (\#12) describe the PH dynamics of a neutralization reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
flow stirred-tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
dynamics of a basic brushed direct current electrical machine.

The \textit{Flexbeam} benchmark (\#14) is a plant employed in vibration studies; the 
physical  system consists of a flexible metallic structure with piezoceramic 
actuators and sensors. The \textit{guidance chen} benchmark (\#15) is another 
high-order system model used by Chen et al.~\cite{CHEN1979389}  to evaluate 
model order reduction techniques; it corresponds to a guidance control system model,
which is used to determine the path of an autonomous vehicle movement. The 
\textit{helicopter} benchmark plant (\#16) describes the dynamics of transitional motion 
with respect to a longitudinal plane and the rotational motion around the longitudinal 
axis for a coaxial helicopter.

The benchmarks \textit{Invpendulum\_cartpos} (\#17) and \textit{Invpendulum\_pendang} (\#18)
are models for the cart position and the pendulum angle of an inverted pendulum 
plant composed by a point mass, which must be equilibrated above the pivot point and is 
mounted on an one degree of freedom cart that moves over a track through a DC motor.

The \textit{magpointer} (\#19) corresponds to a magnetic pointer plant composed by a pointer 
employed in analogue gauges and indicators, whose angular position dynamics is 
controlled by a magnetic field. The \textit{magsuspension} describes (\#20) the dynamic of
a magnetic car suspension system. The \textit{pendulum} (\#21) plant consists of a swinging 
point mass suspended from a frictionless pivot by means of a negligible mass rod.

The \textit{Regulator} (\#22) plant consists of a linear model of a synchronous electrical
machine connected to an infinite bus~\cite{KOKOTOVIC198023}. The 
\textit{springer-mass damper system} plant (\#23) is a classic model for several mechanical 
systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark (\#24) describes the linear model for the level dynamics 
of a  boiler steam drum~\cite{boiler}.

The \textit{suspension} (\#25) benchmark corresponds to the model of a single wheel suspension 
system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
which connects the car to one of its wheels.  The \textit{tapedriver} benchmark (\#26)
corresponds to the model of a computer tape driver, \textit{i.e.}, a computer storage device 
used to read and write data on magnetic tapes.

>>>>

@@

%There are two continuous stirred tank reactor models named 
\textit{cstr} (\#11) and \textit{cstrtmp} (\#12) describe the PH dynamics of a reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a reaction~\cite{astrom2006advanced} in a 
%continuous flow stirred-
tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
dynamics of a 
%basic brushed 
direct-current electrical machine.

The \textit{Flexbeam} benchmark (\#14) is 
%a plant 
employed in vibration studies and models  
%the physical system consists of 
a flexible metallic structure with sensors and actuators. 
The \textit{guidance chen} benchmark (\#15) is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
model-order reduction techniques; it models a guidance control system, 
which is used to determine the path of an autonomous vehicle. 
The \textit{helicopter} benchmark plant (\#16) describes the transitional and rotational dynamics 
%of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
of a coaxial helicopter.

\textit{Invpendulum\_cartpos} (\#17) and \textit{Invpendulum\_pendang} (\#18) 
are models for the cart position and the angle of an inverted pendulum placed on the cart,  
%plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
which moves over a track through a DC motor.

The \textit{magpointer} (\#19) describes a magnetic pointer, 
% plant composed by a pointer employed in analogue gauges and indicators, 
whose angular position dynamics is controlled by a magnetic field. 
The \textit{magsuspension} describes (\#20) the dynamic of a magnetic car suspension system. 
The \textit{pendulum} (\#21) plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.

The \textit{Regulator} (\#22) consists of a linear model of a synchronous electrical machine% connected to an infinite bus
~\cite{KOKOTOVIC198023}. 
The \textit{springer-mass damper system} plant (\#23) is a standard model for the dynamics of several mechanical systems. 
%This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark (\#24) describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}.

The \textit{suspension} (\#25) models a single-wheel suspension system of a car, 
namely the relative motion dynamics of a mass springer damp model, which connects the car to one of its wheels.  
The \textit{tapedriver} benchmark (\#26) models a computer tape driver, 
that is a computer storage device used to read and write data on magnetic tapes.
